Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Improve reproducibility by fetching R package versions in-text

The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' (version 2.15.0) [@Burkner2018] and posterior fits using `pp_check()`  (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version 1.8.1) [@Gabry2019].

@@

Data were visualised using 'ggplot2' (version 3.3.5) [@Wickham2016], 'ggpubr' (version 0.4.0) [@Kassambara2020] and patchwork (version 1.1.1) [@Pedersen2020].

>>>>

The statistical analysis was performed using R version `r version$version.string` [@RCT2022] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

@@

Model finesses were evaluated using model summaries and diagnostic plots from 'brms' 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' ((version `r packageVersion("bayesplot")`)) [@Gabry2019].

@@

Data were visualised using 'ggplot2' ((version `r packageVersion("ggplot2")`)) [@Wickham2016], 'ggpubr' ((version `r packageVersion("ggpubr")`)) [@Kassambara2020] and patchwork ((version `r packageVersion("patchwork")`)) [@Pedersen2020].

All methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
